\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{ulem} 

\input{glyphtounicode}


%----------FONT OPTIONS---------- 
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
% \begin{center}
%     \textbf{\Huge \scshape Isaiah Aganon} \\ \vspace{1pt}
%     \small +1 (365) 880-9158 $|$ 
%     \href{https://webpage-aganonisaiahs-projects.vercel.app/}{\underline{IsaiahAganon.app}} $|$
%     \href{mailto:IsaiahAganon@cmail.carleton.ca?subject=Re:%20Internship%20Application%20Status&body=Hello%20Isaiah,}{\underline{IsaiahAganon@cmail.carleton.ca}} $|$
%     \href{https://www.linkedin.com/in/isaiah-aganon-888b892a8/}{\underline{linkedin/IsaiahAganon}} $|$
%     \href{https://github.com/AganonIsaiah}{\underline{github/AganonIsaiah}}
% \end{center}

\begin{center}
  \textbf{\Huge \scshape Isaiah Aganon} \\ \vspace{1pt}
  \small
  \faPhone\ +1 (365) 880-9158  
  \hspace{5pt}
  \faEnvelope\ \href{mailto:IsaiahAganon@cmail.carleton.ca?subject=Re:%20Internship%20Application%20Status&body=Hello%20Isaiah,}{\uline{IsaiahAganon@cmail.carleton.ca}} 
  \hspace{5pt}
  \faGlobe\ \href{https://webpage-aganonisaiahs-projects.vercel.app/}{\uline{Website}}
  \hspace{5pt}
  \faLinkedin\ \href{https://www.linkedin.com/in/isaiah-aganon-888b892a8/}{\uline{LinkedIn}}
  \hspace{5pt}
  \faGithub\ \href{https://github.com/AganonIsaiah}{\uline{GitHub}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Carleton University}{2027 (Expected)}
      {Bachelor of Computer Science (Honours), Minor in Mathematics}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{{\bf Specialization}: Artificial Intelligence \& Machine Learning}
        \resumeItem{{\bf GPA}: 89.4\% (A)}
        % \resumeItem{{\bf Deans' Honour List}: 2022 -- 2024}
       \resumeItem{{\bf Relevant Courswork}: Abstract Data Types \& Algorithms, Object-Oriented Software Engineering, Design \& Analysis of Algorithms, Discrete Structures I \& II, Database Management Systems, Operating Systems}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading{RBC\textnormal{ $|$ \textit{Software Developer Intern}}}{May. 2025 -- Dec. 2025}
    {{\textbf{Tech Stack:} JavaScript, React, Java, Spring Boot, PostgreSQL, AWS}}{Toronto, ON}
        \resumeItemListStart    
            \resumeItem{Incoming intern.}
        \resumeItemListEnd
    
    \resumeSubheading{Carleton University\textnormal{ $|$ \textit {Teaching Assistant (Fundamentals of Web Applications)}}}{Jan. 2025 -- Present}
    {{\textbf{Tech Stack:} JavaScript, HTML, CSS, SQLite, Node.js, Express.js, React}}{Ottawa, ON}
        \resumeItemListStart
            \resumeItem{Delivered weekly tutorials for a class section of 33 students, covering web development using HTML, CSS,
            JavaScript, SQLite, and Node.js for back-end development.}
            \resumeItem{Guided students through hands-on projects utilizing Node.js, Express.js, and React, emphasizing RESTful APIs,
            component-based architecture, and state management.}
            \resumeItem{Taught debugging techniques in Node.js and React applications, including using browser DevTools and React
            DevTools for performance tuning and troubleshooting.}
        \resumeItemListEnd

    \resumeSubheading{Carleton University\textnormal{ $|$ \textit{Teaching Assistant (Fundamentals of Web Application)}}}{Sep. 2024 -- Dec. 2024}
    {{\textbf{Tech Stack:} JavaScript, TypeScript, HTML, CSS, SQLite, Deno, Tailwind CSS}}{Ottawa, ON}
        \resumeItemListStart
            \resumeItem{Conducted weekly tutorials for a class section of 47 students, focusing on web development fundamentals, including
            HTML, CSS, JavaScript, SQLite, and Deno for back-end development.}
            \resumeItem{Introduced students to Deno’s Fresh framework, TypeScript, and Tailwind CSS, guiding them through the process
            of building a full-stack web application project, integrating front-end and back-end components.}
            \resumeItem{Assisted students with using Chrome DevTools to inspect elements, debug JavaScript errors, and analyze network
            requests for failed API calls, ensuring faster resolution to programming challenges.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
 \resumeSubHeadingListStart

 \resumeProjectHeading{\href{https://github.com/AganonIsaiah/Webpage-App}
 {{\faGithub} {\bf Digital Profile App} $|$ {\textit{JavaScript, Node.js, React, CSS, Vercel}}}} {}
    \resumeItemListStart
      \resumeItem{Created an iMessage-styled digital profile webpage with React and Node.js, displaying interactive, command-based messages that showcase my biography, resume, work experience, and projects.}
      \resumeItem{Deployed the application on Vercel, leveraging its severless architecture for fast performance, automatic scaling, and seamless CI/CD integration.}
    \resumeItemListEnd

    % \resumeProjectHeading{
    % \href{https://github.com/AganonIsaiah/Calendar-App}
    % {{\faGithub} {\bf Calendar App} $|$ {\textit{JavaScript, Node.js, Express.js, PostgreSQL, React, CSS}}}} {}
    % \resumeItemListStart
    % \resumeItem{Developed a full-stack calendar application with React and Node.js, enabling users to manage events while displaying local time and weather data via OpenWeatherMap API.}  
    % \resumeItem{Implemented secure authentication and event storage with Express.js and PostgreSQL, ensuring persistent user data and personalized access.}
    % \resumeItemListEnd 

 \resumeProjectHeading{
    \href{https://github.com/AganonIsaiah/French-Learning-App}
    {{\faGithub} {\bf French Speaking App} $|$ {\textit{Java, Spring Boot, HTML, CSS}}}} {}
    \resumeItemListStart
        \resumeItem{Designed and implemented a full-stack web application leveraging Spring Boot to support French language learners
        in practicing and receiving feedback on their oral production skills.}
        \resumeItem{Integrated third-party APIs, including Voice RSS for text-to-speech functionality and AssemblyAI for advanced
        speech analysis, providing users with real-time pronunciation and fluency feedback.}
    \resumeItemListEnd

    \resumeProjectHeading{
      \href{https://github.com/AganonIsaiah/DSA-Visualizer-App}
      {{\faGithub} {\bf Data Structures \& Algorithms Visualizer App} $|$ {\textit{React, JavaScript, Spring Boot, Java, Vercel, Heroku}}}} {}
      \resumeItemListStart
      \resumeItem{Developed an interactive front-end using React to visualize data structures and algorithms with step-by-step animations, ensuring a seamless user experience.}
  \resumeItem{Implemented a Spring Boot back-end to handle user interactions, efficiently manage data flow, and support algorithm visualizations with minimal latency.}
  \resumeItemListEnd

    % \resumeProjectHeading{
    % \href{https://github.com/AganonIsaiah/Music-Listening-App}
    % {{\faGithub} {\bf Music Playlist App} $|$ {\textit{JavaScript, Node.js, Handlebars.js, SQLite}}}} {}
    % \resumeItemListStart
    %     \resumeItem{Developed a dynamic full-stack music management application with a Handlebars.js front-end and Node.js
    %     back-end, allowing users to create, organize, and manage personalized music playlists.}
    %     \resumeItem{Utilized the YouTube Data API v3 to fetch music data and implemented SQLite for persistent storage of playlists
    %     and music preferences.}
    % \resumeItemListEnd 
    

    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Java, JavaScript, TypeScript, C, C++, SQL} \\
     \textbf{Frameworks \& Libraries}{: React, Node.js, Deno, Express.js, Spring Boot, Tailwind CSS} \\
     \textbf{Developer Tools}{: Git, Docker, Linux, AWS, Vim, VS Code, IntelliJ, Vercel} \\
    % \textbf{Spoken Languages}{: English (Native), French (Limited Working Proficiency)}
   
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
